A Comparison of Use-Case Based and Checklist- Based Reading: A Controlled Experiment

### 2015-03-19 rmtw/a6/latex8.tex
Added citations

\subsection{Software Evolution}

>>>>

API design is notoriously difficult, a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{bloch2008effective},\cite{afonso2012evaluating}, \cite{stylos2006comparing}. Some studies have created a generalisable usability study with the aim of analysing the design decisions taken when creating an API \cite{}. Another empirical study, which involved working with 25 programmers, highlighted API design problems such as assigning names to API features and difficulty in naming types \cite{shi2011empirical}. The study also found that in order to create a usable API, one must ensure that the API is understandable via good documentation, it’s not too abstract, has high reusability and that it is easy to learn \cite{shi2011empirical}. Both studies also highlighted that API designers must ensure that, when using design patterns, such as the concrete factory pattern, that the intent of the API is clear to the user \cite{shi2011empirical},\cite{stylos2006comparing}.

A further study involved combining semiotic and cognitive methods to evaluate APIs as a means of facilitating communication, via an artefact, between programmers and designers. \cite{afonso2012evaluating}. However, these studies do not highlight the actual reasons behind changes of APIs.

\subsection{API Change}
Previous studies that have attempted to identify the reason behind API changes have primarily focused APIs that are a part of large programming languages, such as Java and Smalltalk \cite{robbes2012developers}, \cite{shi2011empirical}, \cite{hou2011exploring}. The intent of the study was to uncover the intents behind the changes made in the AWT/Swing Java libraries. The study found that the use of a strong architecture was vital in ensuring a smooth evolution of the API \cite{hou2011exploring}.

However, when APIs are changed, problems tend to occur. One study investigated three frameworks and one library in which the study found that 80\% of re-factoring changes to APIs negatively affected existing applications. Re-factorings are not the only changes to APIs that can impact existing projects negatively. Another study was conducted regarding the changes, or, ripple effect that changes in APIs have on an entire ecosystem. This particular empirical study found that 14\% of non-trivial API deprecations caused errors in at least one project, with the worst case of 79 projects being affected \cite{robbes2012developers}.

Furthermore, a study of the impact of reliable APIs was undertaken in the Android ecosystem \cite{mcdonnell2013empirical}. The study aimed to discover if APIs with high rates of faults affected the success of an application. The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{mcdonnell2013empirical}.
